MSc Thesis

### 2023-05-08 manuscript/main.tex
added a few things to the results of qtl chapter

Of the approximately 1700 plants planted, [1300] produced enough leaf material for analysis. After pooling, we were left with 359 samples across three environments. Silicon content in \textit{Aegilops tuaschii} ranged from 0.784\% to 11.473\%. There were notable differences in silicon content based on the growing environment. The glasshouse plants averaged 1.450\% $\pm$ 0.032 (SE), while the two outdoor environments averaged 4.935\% $\pm$ 0.108 and 6.471\% $\pm$ 0.132. Silicon and manganese showed significant positive correlation ($\beta = 0.278\pm0.051, z = 5.46, p<0.0001$) (Figure \ref{Fig:mn_si_regression}). Overall, my analysis revealed no regions of the \textit{Aegilops tauschii} genome that have significant associations across environments with silicon content (Figure \ref{Fig:si_peak_plot}). For manganese, we detected a number of peaks in each environment that exceeded the threshold for significance. However, when comparing accross environments, we found no regions that consistently exceeded the threshold significance. We did however find 11 regions exceeding the significance threshold that were present in both of our growing environments with real soil.  were three that had pronounced peaks relative to the average response (Figure \ref{Fig:mn_peak_plot}). Within the plants, silicon and manganese content were correlated ($R^2_m = 0.05, R^2_c = 0.35 , p < 0.0001$) (Figure 3).

>>>>

Of the approximately 1700 plants planted, [1300] produced enough leaf material for analysis. After pooling, we were left with 359 samples across three environments. Silicon content in \textit{Aegilops tuaschii} ranged from 0.784\% to 11.473\%. There were notable differences in silicon content based on the growing environment. The glasshouse plants averaged 1.450\% $\pm$ 0.032 (SE), while the two outdoor environments averaged 4.935\% $\pm$ 0.108 and 6.471\% $\pm$ 0.132. Silicon and manganese showed significant positive correlation ($\beta = 0.278 \pm 0.051, z = 5.46, p<0.0001, R^2_{marginal} = 0.05, R^2_{conditional} = 0.35 $) (Figure \ref{Fig:mn_si_regression}). Overall, my analysis revealed no regions of the \textit{Aegilops tauschii} genome that have significant associations across environments with silicon content (Figure \ref{Fig:si_peak_plot}), nor for manganese content (Figure \ref{Fig:mn_peak_plot}). For manganese, we detected a number of peaks in each environment that exceeded the threshold for significance. However, when comparing accross environments, we found no regions that consistently exceeded the threshold significance. We did however find 11 regions exceeding the significance threshold that were present in both of our growing environments with real soil.
\section{Discussion}
